A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-07 main.tex
Wrote a paragraph on Specialized Code Problem.

\subsubsection{行列計算も高速化できる}

Multistage calculi can also optimize matrices calculation.

\subsubsection{生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
このため、間違って組み合わせると容易にエラーを引き起こす。既存の型システムではこのエラーを防止できない}

Generated code is specialized for a given size of matrix and we cannot use it for different sizes.
We call this problem \red{Specialized Code Problem}.

>>>>

% \subsubsection{ベクトル計算も高速化できる}

Multistage programming can also optimize vector calculation.
For example, \verb|add| function, which takes two vectors and return the sum of them,
is impremented with loop in many cases.
We can unroll \verb|add| function for a given vector length and optimize it with multistage programming.
\red{MetaOCamlで書いた長さ付きベクトルの例?}

% \subsubsection{生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
% このため、間違って組み合わせると容易にエラーを引き起こす。既存の型システムではこのエラーを防止できない}

Although unrolled \verb|add| function is optimzied, we cannot use it for different vector length.
For example, when you optimize for the length of 5, you shoudn't use it for vectors of 3 lengths.
This problem is serious but existing type systems for multistage calculi cannot prevent it.

% We call this problem \red{Specialized Code Problem}.
